PDBF Documentation

### 2015-08-07 pdbf-doc.tex
Update pdbf-doc.tex

\noindent PDBF files are created from LaTeX source code and a relational database. The raw data can either be a SQL statement string, a file with SQL statements, or contained in a database (currently PostgreSQL/MySQL/MariaDB supported). In the LaTeX code you can then specify how the PDBF element (currently charts/pivot tables/multiplot charts/sql statements are supported) is created from the raw data with options and an SQL query. Read more in the \href{http://uds-datalab.github.io/PDBF/}{documentation}, which is itself is a PDBF document.\\

>>>>

\noindent PDBF files are created from LaTeX source code and a relational database. The raw data can either be a SQL statement string, a file with SQL statements, or contained in a database (currently PostgreSQL/MySQL/MariaDB supported). In the LaTeX code you can then specify how the PDBF element (currently charts/pivot tables/multiplot charts/sql statements/dataTexts/dataTables are supported) is created from the raw data with options and an SQL query. Read more in the \href{http://uds-datalab.github.io/PDBF/}{documentation}, which is itself is a PDBF document.\\
